### 2021-11-17 manuscript/hiv-gwas.tex
Update on Overleaf.

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=0.462\linewidth]{figures/model_figure}
		\caption{The POUMM statistical model for the spVL trait. (A) shows how the pathogen effect on spVL, $g_v$, evolves according to an OU process along (C) the pathogen phylogeny. The dashed line in (A) shows the expected value of the trait at each point in time under the model. (B) shows that the non-pathogen effect on spVL, $e$, is modeled as a Gaussian random variable. Each tip on the phylogeny corresponds to a sampled individual with an independent non-pathogen-effect drawn from the distribution shown in (B).}
		\label{fig:spVLModel}
	\end{center}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.462\linewidth]{figures/spvl_calculation_comparison.png}
	\caption{A comparison of different ways to calculate spVL based on viral load measurements provided by the SHCS. The stricter filtering excludes all measurements possibly $<$ 6 months after infection and after treatment or AIDS, whereas the more lenient filtering excludes only measurements after treatment. We used the lenient filter, mean measurement values because these correlate well with the values from the stricter filter but allow us to retain many more individuals from the cohort for our study.}
	\label{fig:spvl-calc-comparison}
	\end{center}
\end{figure}

>>>>

\begin{figure}[H]
	\begin{center}
	\includegraphics[width = \linewidth]{figures/simulation_setup.png}
% 		\includegraphics[width=0.462\linewidth]{figures/model_figure}
% 		\caption{The POUMM statistical model for the spVL trait. (A) shows how the pathogen effect on spVL, $g_v$, evolves according to an OU process along (C) the pathogen phylogeny. The dashed line in (A) shows the expected value of the trait at each point in time under the model. (B) shows that the non-pathogen effect on spVL, $e$, is modeled as a Gaussian random variable. Each tip on the phylogeny corresponds to a sampled individual with an independent non-pathogen-effect drawn from the distribution shown in (B).}
		\label{fig:spVLModel}
	\end{center}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.7\linewidth]{figures/spvl_calculation_comparison.png}
	\caption{A comparison of different ways to calculate spVL based on viral load measurements provided by the SHCS. The stricter filtering excludes all measurements possibly $<$ 6 months after infection and after treatment or AIDS, whereas the more lenient filtering excludes only measurements after treatment. We used the lenient filter, mean measurement values because these correlate well with the values from the stricter filter but allow us to retain many more individuals from the cohort for our study.}
	\label{fig:spvl-calc-comparison}
	\end{center}
\end{figure}
